---
title: "Unbounded Implicit Learning - Detailed Analysis"
author: "Shanaathanan Modchalingam"
date: "July 2, 2019"
output: 
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    
---

```{r setup, include=FALSE, warning=FALSE}
source("analysisFunctions.R")
library(tidyverse)
library(ggbeeswarm)
```

# Some backround

A few studies show that implicit adaptation is 'rigid'. 
'Rigid' in this context means an upper boundary on adaptation.

These studies include (but are not limited to)

### Bond & Taylor (2015)
Here, people adapted to visuomotor rotations and provided aiming directions __prior__ to every reach. 
Implicit learning was measured by subtracting the aiming direction from the direction of movement.  

__Movement type:__ Balistic movements (<400 ms) and end-point feedback  
__Target parameters:__ 7 cm distance, radial target locations    
__Other:__ Participants were reminded "always moving directly to the target may not be effective" every 40 trials  

__Interesting tidbits:__ training to 1 target actually  resulted in higher implicit learning (30°!). 
2 and 4 targets resulted in 17 - 20°.  
Final implicit learning was ~10° for 15, 30, 60 and 90° rotations -- this did not differ between groups.


### Kim et al. (2019)
Here, people adapted to a constant visual error. That is, the error was present and consistent, regardless 

__Movement type:__ Clamped. Slicing movements (<300 ms)  
__Target parameters:__ 8 cm distance, radial target locations, 8 targets (in exp 1) or 4 targets (in exp 2)  
__Other:__ Patricipants were instructed to ignore the visual error.

__Interesting tidbits:__ 


### Modchalingam et al. (20??)

__Movement type:__ Non-balistic  
__Target parameters:__ 12 cm distance, located 45, 90, 135 degrees in polar coordinates  
__Other:__ 

__Interesting tidbits:__ 

# No-cursor analysis

First, we analyze the no-cursor data. Here-in lies our main question; do implicit aftereffects

## Preprocessing

### Load the omnibus data file

First, we will load in the omnibus dataframe. This dataframe contains every no-cursor reach for every participant, including during the aligned training phase. Below is a sample of the dataframe.  

```{r, cols.print = 10, warning=FALSE}

omnibus_nocur <- read_delim("data/omnibus/omnibus_nocur.csv", 
                            delim = ",", 
                            col_types = cols(.default = col_double(), 
                                             task_num = col_factor(),
                                             trial_num = col_factor(),
                                             rotation_angle = col_factor(),
                                             targetangle_deg = col_factor(),
                                             ppt = col_character(),
                                             stratuse = col_factor(),
                                             exp = col_character()))

head(omnibus_nocur)

```

The column of interest is "angular_dev". It contains, in degrees, the amount participants deviated from a straight-line reach towards the target.   

### Baseline correction

The first thing we will do is correct for baseline deviations in training.  
To do this, we will subset the above dataframe into 2 dataframes; one containing data from only the rotated session, and one containing data from only the aligned session.  

```{r}
rot_nocur <- filter(omnibus_nocur, rotation_angle != 0)

head(rot_nocur)
```

```{r}
bl_nocur <- filter(omnibus_nocur, rotation_angle == 0)

head(bl_nocur)
```

Next, we need to apply a function to the rotated-session data. From each angular deviation, we will subtract the mean angular deviation of all baseline angular deviations that share the same participant and target angle. 

The functions is as follows. 

```{r}
apply_blcorrection <- function(rot_df_row, bl_df){
  
  # make sure input is in format: targetangle_deg, ppt, angular_dev

  bl <- filter(bl_df, 
               targetangle_deg == rot_df_row[1] & 
                 ppt == rot_df_row[2])$angular_dev %>% 
    mean(na.rm = TRUE)

  
  corrected_dev <- as.numeric(rot_df_row[3]) - bl
  
  return(corrected_dev)
}
```

Applying the above function to rotated-session-data.

```{r}
rot_nocur$temp <- select(rot_nocur, targetangle_deg, ppt, angular_dev) %>%
  apply(1, FUN = apply_blcorrection, bl_df = bl_nocur)

# rename some columns
rot_nocur <- rot_nocur %>% 
  rename(raw_angular_dev = angular_dev) %>%
  rename(angular_dev = temp)

head(rot_nocur)
```

We now have an angular deviation column that is baseline corrected. We will use the _rot_nocur_ dataframe from now on.

__We might want to use group by to get participant means!__

Now we will get a mean for each participant

```{r}
nocur_summary <- rot_nocur %>%
  group_by(exp, ppt, rotation_angle, stratuse) %>%
  summarise(mean_devs = mean(angular_dev), sd = sd(angular_dev), ci = vector_confint(angular_dev))

nocur_summary
```


## Visualizing the data


```{r}
p <- nocur_summary %>%
  filter(exp == 'abruptExp') %>%
  group_by(stratuse) %>%
  summarise(mean_dev = mean(mean_devs), ci = vector_confint(mean_devs)) %>%
  ggplot(aes(stratuse, mean_dev, colour = "mean + ci")) +
  geom_beeswarm(data = filter(nocur_summary, exp == 'abruptExp'), 
                aes(y = mean_devs, colour = "individual ppts"),
                size = 3, alpha = 0.2) +
  geom_linerange(aes(ymin = mean_dev - ci, ymax = mean_dev + ci),
                 lwd = 3, alpha = 0.4) +
  geom_point(size = 3, alpha = 1) +
  scale_y_continuous(limits = c(-5, 60), 
                     breaks = c(0, 15, 30, 45, 60), 
                     name = "hand deviation (°)") +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  scale_color_manual(values=c("#000000", "#FFA47E"))

  
  # geom_beeswarm(data = noCur60, aes(x = 85 + 5, y = deviation), size = 3, alpha = 0.6) +
  # geom_beeswarm(data = noCurMedians, aes(x = rot + 5, y = meanDeviation), size = 3, alpha = 0.6) +
  # geom_point(size = 14, alpha = 1) +
  # geom_linerange(aes(ymin = meanDeviation - ci, ymax = meanDeviation + ci),
  #                 lwd = 20, alpha = 0.4) +
  # geom_point(size = 14, data = abruptNoCurSummary, aes(x = 85, y = deviation), alpha = 1) +
  # geom_linerange(data = abruptNoCurSummary, aes(x = 85, y = deviation, ymin =deviation - ci, ymax = deviation + ci),
  #                 lwd = 20, alpha = 0.4) +
  # scale_x_continuous(limits = c(10, 95), 
  #                    breaks = c(15, 30, 45, 60, 85), 
  #                    labels = c(15, 30, 45, 60, 60), name = "rotation size") +
  # scale_color_manual(values=c("#FFA47E", "#00BFC4"), name="Strategy Use",
  #                    breaks=c("exc", "inc"),
  #                    labels=c("without strategy", "with strategy"))
  # theme(text = element_text(size=40), 
  #       axis.text = element_text(size=40), 
  #       legend.text = element_text(size=48))

  
p
```

We are interested in whether...