---
title: "Unbounded Implicit Learning - Analysis"
author: "Shanaa Modchalingam"
date: '2022-04-04'
output: 
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    
---

```{r setup, include=FALSE, warning=FALSE}
rm(list = ls())      # clean environment

source("src/helper_funcs.R")
library(data.table)
library(tidyverse)
library(ggbeeswarm)
library(ez) #for ANOVAs
library(effectsize) # for eta-squared
library(BayesFactor)
library(bayestestR)

```

# Some backround

A few studies show that implicit adaptation is 'rigid'. 
'Rigid' in this context means an upper boundary on adaptation.

These studies include (but are not limited to)

### Bond & Taylor (2015)
Here, people adapted to visuomotor rotations and provided aiming directions __prior__ to every reach. 
Implicit learning was measured by subtracting the aiming direction from the direction of movement.  

__Movement type:__ Balistic movements (<400 ms) and end-point feedback  
__Target parameters:__ 7 cm distance, radial target locations    
__Other:__ Participants were reminded "always moving directly to the target may not be effective" every 40 trials  

__Interesting tidbits:__ training to 1 target actually  resulted in higher implicit learning (30째!). 
2 and 4 targets resulted in 17 - 20째.  
Final implicit learning was ~10째 for 15, 30, 60 and 90째 rotations -- this did not differ between groups.


### Kim et al. (2019)
Here, people adapted to a constant visual error. That is, the error was present and consistent, regardless 

__Movement type:__ Clamped. Slicing movements (<300 ms)  
__Target parameters:__ 8 cm distance, radial target locations, 8 targets (in exp 1) or 4 targets (in exp 2)  
__Other:__ Patricipants were instructed to ignore the visual error.

__Interesting tidbits:__ 


### Modchalingam et al. (2019)

__Movement type:__ Non-balistic  
__Target parameters:__ 12 cm distance, located 45, 90, 135 degrees in polar coordinates  
__Other:__ 

__Interesting tidbits:__ 

# No-cursor analysis

First, we analyze the no-cursor data. Here-in lies our main question; do implicit aftereffects

## Load and summarize data

### Load the baseline corrected data

Load in the data frame, then separate for easier plotting

```{r, cols.print = 10, warning=FALSE}
# load in the large df
rot_all <- read_delim("data/bl_corrected/bl_corrected_data.csv", 
                               delim = ",", 
                               col_types = cols(.default = col_double(),
                                                targetangle_deg = col_factor(),
                                                strat_use = col_factor(),
                                                ppt = col_factor(),
                                                exp = col_factor(),
                                                block_num = col_factor(),
                                                trial_set = col_factor(),
                                                reach_type = col_factor()))

# separate the nocursor and training data
rot_nocur <- rot_all %>%
  filter(reach_type == "nocursor")

rot_training <- rot_all %>%
  filter(reach_type == "reach")
```
```{r, cols.print = 10, warning=FALSE}
# palette
cbp1 <- c("#ff8000", "#e51636", "#0500a0")

```

The column of interest is "angular_dev". It contains, in degrees, the amount participants deviated from a straight-line reach towards the target.   


### Make a summary file with means for each participant

Each participant has 8 means: 2 for each block (one for each strategy use)
```{r}
nocur_summary <- rot_nocur %>%
  group_by(exp, ppt, block_num, strat_use) %>%
  summarise(mean_devs = mean(angular_dev), 
            sd = sd(angular_dev), 
            ci = vector_confint(angular_dev),
            n = n(), .groups = "drop")

head(nocur_summary)
```

## Statistics

### OMNIBUS ANOVA
We do a 3x4x2 mixed ANOVA (experiment x block x strategy use)
```{r, include=FALSE}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- nocur_summary %>%
  ezANOVA(wid = ppt,
        dv = mean_devs, 
        within = .(block_num, strat_use),
        between = exp,
        detailed = TRUE)
```
```{r}
#show and ANOVA + assumptions
print(temp_ANOVA$ANOVA)
```


### Implicit aftereffects
We will do 2 sets of analyses for all sets of data. First, we compare our measures in blocks where they first hit 60-degree rotations. Then, we compare block 4 in all groups (time = same).

*3x4 ANOVA (experiment x block)*
```{r, include=FALSE}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- nocur_summary %>% 
  filter(strat_use == '0') %>%
  ezANOVA(wid = ppt,
        dv = mean_devs, 
        within = .(block_num),
        between = exp,
        detailed = TRUE)
```
```{r}
#show and ANOVA + assumptions
print(temp_ANOVA$ANOVA)
```

To test whether the method of perturbation onset effected implicit learning, we compared the aftereffects of learning in No-Strategy trials.

*Early Implicit Aftereffects*
These are aftereffects measured during the blocks in which participants first encounter a 60-degree rotation.
```{r}
wo_strat_init_blocks <- nocur_summary %>% 
  filter(strat_use == '0') %>% #only the implicit aftereffects
  filter((exp == 'stepped' & block_num == '4') | #only the 5 blocks (1 and 4)
         (exp == 'abrupt' & block_num == '1') |
         (exp == 'ramped' & block_num == '1'))

```

Plot
```{r}
plot_desc_group_density(wo_strat_init_blocks, "exp", "mean_devs", title = "A. Initial Implicit Aftereffects")
```
Descriptive stats
```{r}
wo_strat_init_blocks %>% 
  group_by(exp) %>%
  summarise(mean = mean(mean_devs), 
            sd = sd(mean_devs), 
            ci = vector_confint(mean_devs),
            n = n())
```
ANOVA and post-hoc test
```{r}
temp_ANOVA <- aov(mean_devs ~ exp, data = wo_strat_init_blocks)

#show ANOVA + assumptions
print(summary(temp_ANOVA), digits = 6)
eta_squared(temp_ANOVA)
TukeyHSD(temp_ANOVA)
```
Bayes Factors
```{r, include=FALSE}

tmp_bf_abr_ramp <- bayes_t_test(wo_strat_init_blocks, "exp", "abrupt", "ramped", "mean_devs")
tmp_bf_stp_ramp <- bayes_t_test(wo_strat_init_blocks, "exp", "stepped", "ramped", "mean_devs")
tmp_bf_stp_abr <- bayes_t_test(wo_strat_init_blocks, "exp", "stepped", "abrupt", "mean_devs")
```
```{r}
bf <- anovaBF(mean_devs ~ exp, data = wo_strat_init_blocks, progress=FALSE)
print(bf)
bayesfactor_inclusion(bf)
print(tmp_bf_abr_ramp)
print(tmp_bf_stp_ramp)
print(tmp_bf_stp_abr)
```



2. Time-constant measures

```{r}
wo_strat_final_blocks <- nocur_summary %>% 
  filter(strat_use == '0') %>% #only the implicit aftereffects
  filter(block_num == '4') # only comparing block 4 data
```
```{r}
#plot
plot_desc_group_density(wo_strat_final_blocks, "exp", "mean_devs", title = "B. Block 4 Implicit Aftereffects")
```
```{r}
# descriptives
wo_strat_final_blocks %>% 
  group_by(exp) %>%
  summarise(mean = mean(mean_devs), 
            sd = sd(mean_devs), 
            ci = vector_confint(mean_devs),
            n = n())
```
```{r}
no_cur_ANOVA <- aov(mean_devs ~ exp, data = wo_strat_final_blocks)

#show ANOVA + assumptions
print(summary(no_cur_ANOVA), digits = 6)
eta_squared(no_cur_ANOVA)
TukeyHSD(no_cur_ANOVA)
```
Bayes Factors
```{r, include=FALSE}

tmp_bf_abr_ramp <- bayes_t_test(wo_strat_final_blocks, "exp", "abrupt", "ramped", "mean_devs")
tmp_bf_stp_ramp <- bayes_t_test(wo_strat_final_blocks, "exp", "stepped", "ramped", "mean_devs")
tmp_bf_stp_abr <- bayes_t_test(wo_strat_final_blocks, "exp", "stepped", "abrupt", "mean_devs")
```
```{r}
anovaBF(mean_devs ~ exp, data = wo_strat_final_blocks, progress=FALSE)
print(tmp_bf_abr_ramp)
print(tmp_bf_stp_ramp)
print(tmp_bf_stp_abr)
```


### Explicit strategy
Same analysis pipeline as for the implicit measures

First, we need to actually calculate strategy
```{r}
#first get explicit strat for each ppt

nocur_summary_wide <- nocur_summary %>%
  select(-sd, -ci) %>%
  pivot_wider(names_from = "strat_use", 
              values_from = mean_devs, 
              names_prefix = "strat_") %>%
  mutate(strategy = strat_1 - strat_0)
```

1. Initial measures
```{r}
strat_initial_blocks <- nocur_summary_wide %>% 
  filter((exp == 'stepped' & block_num == '4') | #only the 5 blocks (1 and 4)
         (exp == 'abrupt' & block_num == '1') |
         (exp == 'ramped' & block_num == '1'))
```
```{r}
#plot
plot_desc_group_density(strat_initial_blocks, "exp", "strategy", title = "A. Initial Strategy")
```
```{r}
# descriptives
strat_initial_blocks %>% 
  group_by(exp) %>%
  summarise(mean = mean(strategy), 
            sd = sd(strategy), 
            ci = vector_confint(strategy),
            n = n())
```
```{r}

no_cur_ANOVA <- aov(strategy ~ exp, data = strat_initial_blocks)

#show ANOVA + assumptions
print(summary(no_cur_ANOVA), digits = 6)
eta_squared(no_cur_ANOVA)
TukeyHSD(no_cur_ANOVA)
```

Bayes Factors
```{r, include=FALSE}

tmp_bf_abr_ramp <- bayes_t_test(strat_initial_blocks, "exp", "abrupt", "ramped", "strategy")
tmp_bf_stp_ramp <- bayes_t_test(strat_initial_blocks, "exp", "stepped", "ramped", "strategy")
tmp_bf_stp_abr <- bayes_t_test(strat_initial_blocks, "exp", "stepped", "abrupt", "strategy")
```
```{r}
anovaBF(strategy ~ exp, data = strat_initial_blocks, progress=FALSE)
print(tmp_bf_abr_ramp)
print(tmp_bf_stp_ramp)
print(tmp_bf_stp_abr)
```


2. Same but for the final block
```{r}
strat_final_blocks <- nocur_summary_wide %>% 
  filter(block_num == '4')
```
```{r}
#plot
plot_desc_group_density(strat_final_blocks, "exp", "strategy", title = "B. BLock 4 Strategy")
```

```{r}
# descriptives
strat_final_blocks %>% 
  group_by(exp) %>%
  summarise(mean = mean(strategy), 
            sd = sd(strategy), 
            ci = vector_confint(strategy),
            n = n())
```

```{r}

no_cur_ANOVA <- aov(strategy ~ exp, data = strat_final_blocks)

#show ANOVA + assumptions
print(summary(no_cur_ANOVA), digits = 6)
eta_squared(no_cur_ANOVA)
TukeyHSD(no_cur_ANOVA)
```
Bayes Factors
```{r, include=FALSE}

tmp_bf_abr_ramp <- bayes_t_test(strat_final_blocks, "exp", "abrupt", "ramped", "strategy")
tmp_bf_stp_ramp <- bayes_t_test(strat_final_blocks, "exp", "stepped", "ramped", "strategy")
tmp_bf_stp_abr <- bayes_t_test(strat_final_blocks, "exp", "stepped", "abrupt", "strategy")
```
```{r}
anovaBF(strategy ~ exp, data = strat_final_blocks, progress=FALSE)
print(tmp_bf_abr_ramp)
print(tmp_bf_stp_ramp)
print(tmp_bf_stp_abr)
```

3. Compare strategy use in blocks 1 and 4 for abrupt and ramp data


```{r}
strat_betwn_block <- nocur_summary_wide %>% 
  filter(block_num == '4' | block_num =='1', exp == 'abrupt' | exp == 'ramped')

plot_desc_group_density(strat_betwn_block, "block_num", "strategy", subgroup = "exp", title = "C. Strategy Use blocks 1 v 4")
```

```{r}
anovaBF(strategy ~ exp * block_num, data = strat_betwn_block, progress=FALSE)
```
```{r}
btwn_block_strat_ANOVA <- aov(strategy ~ exp * block_num, data = strat_betwn_block)
print(summary(btwn_block_strat_ANOVA), digits = 6)
eta_squared(btwn_block_strat_ANOVA)
TukeyHSD(btwn_block_strat_ANOVA)
```



# Reach training analysis

Use bl_corrected data

```{r}

training_summary_per_trial <- rot_training %>%
  group_by(exp, trial_num_cont) %>%
  summarise(mean_devs = mean(angular_dev), sd = sd(angular_dev), 
            ci = vector_confint(angular_dev), .groups = "drop")

#training_summary$rotation_angle <- factor(training_summary$rotation_angle, levels=c("-15", "-30", "-45", "-60"))
training_summary_per_trial$trial_num_cont <- training_summary_per_trial$trial_num_cont - 66

# make trial sets factor

```


## Init vs block 4 tatistics

Plot of relevant groups

```{r}
training_trial_sets_04 <- rot_training %>%
  filter(trial_set == 1 | trial_set == 3) %>%
  group_by(exp, ppt, trial_set) %>%
  summarise(angular_dev_mean = mean(angular_dev), 
            sd = sd(angular_dev), 
            ci = vector_confint(angular_dev),
            n = n(), .groups = "drop")
  # group_by(exp, trial_set) %>%
  # summarise(trial_set_mean = mean(angular_dev_mean), 
  #           sd = sd(angular_dev_mean), 
  #           ci = vector_confint(angular_dev_mean),
  #           n = n(), .groups = "drop")

head(training_trial_sets_04)
```

```{r}
plot_desc_group_density(training_trial_sets_04, "trial_set", "angular_dev_mean", subgroup = "exp", title = "Training trial sets")
```
### Anova for the trial sets
```{r}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- training_trial_sets_04 %>%
  ezANOVA(wid = ppt,
        dv = angular_dev_mean, 
        within = .(trial_set),
        between = exp,
        detailed = TRUE)

temp_ANOVA
```

```{r}
bf_test <- anovaBF(angular_dev_mean ~ exp * trial_set + ppt, data = training_trial_sets_04, whichRandom = "ppt", progress=FALSE)
print(bf_test)
bayesfactor_inclusion(bf_test)
```

```{r}
plot(bf_test)
```


## We confirm that all groups learn by block 4

```{r}
training_final_trial_set <- training_trial_sets_04 %>% 
  filter(trial_set == '3')
```

```{r}
#plot
plot_desc_group_density(training_final_trial_set, "exp", "angular_dev_mean", title = "Block 4 Adaptation")
```

```{r}
# descriptives
training_final_trial_set %>% 
  group_by(exp) %>%
  summarise(mean = mean(angular_dev_mean), 
            norm_mean = mean(angular_dev_mean)/60,
            sd = sd(angular_dev_mean), 
            ci = vector_confint(angular_dev_mean),
            n = n())
```

```{r}

training_ANOVA <- aov(angular_dev_mean ~ exp, data = training_final_trial_set)

#show ANOVA + assumptions
print(summary(training_ANOVA), digits = 6)
eta_squared(training_ANOVA)
TukeyHSD(training_ANOVA)
```

Bayes Factors
```{r, include=FALSE}
test_bf <- anovaBF(angular_dev_mean ~ exp, data = training_final_trial_set, progress=FALSE)

tmp_bf_abr_ramp <- bayes_t_test(training_final_trial_set, "exp", "abrupt", "ramped", "angular_dev_mean")
tmp_bf_stp_ramp <- bayes_t_test(training_final_trial_set, "exp", "stepped", "ramped", "angular_dev_mean")
tmp_bf_stp_abr <- bayes_t_test(training_final_trial_set, "exp", "stepped", "abrupt", "angular_dev_mean")
```
```{r}
print(test_bf)
bayesfactor_inclusion(test_bf)
print(tmp_bf_abr_ramp)
print(tmp_bf_stp_ramp)
print(tmp_bf_stp_abr)
```

## End of block 1 learning

```{r}
training_trial_sets_1 <- rot_training %>%
  filter(trial_set == 2) %>%
  group_by(exp, ppt, trial_set) %>%
  summarise(angular_dev_mean = mean(angular_dev), 
            sd = sd(angular_dev), 
            ci = vector_confint(angular_dev),
            n = n(), .groups = "drop")
  # group_by(exp, trial_set) %>%
  # summarise(trial_set_mean = mean(angular_dev_mean), 
  #           sd = sd(angular_dev_mean), 
  #           ci = vector_confint(angular_dev_mean),
  #           n = n(), .groups = "drop")

head(training_trial_sets_1)
```

```{r, include=FALSE}
# bayes t-test for end of block 1 learning

tmp_bf_abr_ramp <- bayes_t_test(training_trial_sets_1, "exp", "abrupt", "ramped", "angular_dev_mean")

```
```{r}
t.test(angular_dev_mean ~ exp, data = training_trial_sets_1)
print(tmp_bf_abr_ramp)
```


# Combining all data

Plotting all data
```{r}
# make a summary df
rot_all_summary <- rot_all %>%
  group_by(exp, trial_num_cont, strat_use) %>%
  summarise(mean = mean(angular_dev),
            sd = sd(angular_dev), 
            ci = vector_confint(angular_dev),
            n = n(), .groups = "drop")
```

plot
```{r}
p <- rot_all %>% 
  ggplot(aes(trial_num_cont, angular_dev, colour = exp, shape = strat_use)) +
  geom_point(alpha = 0.04)+
  geom_point(data = rot_all_summary, aes(y = mean)) +
  scale_shape_manual(values=c(20, 2))+
  # stat_summary(fun=mean, geom="point", size=3, color="red") +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  scale_y_continuous(limits = c(-20, 90)) +
  ggtitle("All data")

p

# ggsave(p, height = 9, width = 16, device = "svg", filename = "data/paper_figs/all_reaches.svg")
```

Repeat for normalized angular deviations
```{r}
rot_norm_summary <- rot_all %>%
  group_by(exp, trial_num_cont, strat_use) %>%
  summarise(mean = mean(norm_angular_dev),
            sd = sd(norm_angular_dev), 
            ci = vector_confint(norm_angular_dev),
            n = n(), .groups = "drop")
```
plot
```{r}
p <- rot_all %>% 
  ggplot(aes(trial_num_cont, norm_angular_dev, colour = exp, shape = strat_use)) +
  geom_point(alpha = 0.04) +
  geom_point(data = rot_norm_summary, aes(y = mean)) +
  scale_shape_manual(values=c(20, 2))+
  # stat_summary(fun=mean, geom="point", size=3, color="red") +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  ggtitle("All data")

p

# ggsave(p, height = 9, width = 16, device = "svg", filename = "data/paper_figs/all_reaches_norm.svg")
```
# Last block of stepped

```{r}
ind_nocur_stepped_detailed_summary <- rot_nocur %>%
  filter(exp == "stepped", block_num == 4, strat_use == 0) %>%
  group_by(ppt, block_num_detailed) %>%
  summarise(ind_mean = mean(angular_dev), 
            sd = sd(angular_dev), 
            ci = vector_confint(angular_dev),
            n = n(), .groups = "drop")
ind_nocur_stepped_detailed_summary$block_num_detailed <- factor(ind_nocur_stepped_detailed_summary$block_num_detailed)
group_nocur_stepped_detailed_summary <- ind_nocur_stepped_detailed_summary %>%
  group_by(block_num_detailed) %>%
  summarise(mean_devs = mean(ind_mean), 
            sd = sd(ind_mean), 
            ci = vector_confint(ind_mean),
            n = n(), .groups = "drop")

group_nocur_stepped_detailed_summary
```
```{r}
#plot
plot_desc_group_density(ind_nocur_stepped_detailed_summary, "block_num_detailed", "ind_mean", title = "Block 4 Stepped - no decay")
```

# Decay Slopes

```{r}
    # load in the DECAY data
    data <- load_bl_corrected("data/bl_corrected/bl_corrected_data.csv",
        type = "nocursor"
    )

    # add a column with 1-9 repeating
    data <- data %>%
        mutate(trial_in_block = rep(1:9, length.out = nrow(data)))

    # select useful columns
    data <- data %>%
        select(exp, ppt, strat_use, block_num, trial_in_block, angular_dev) %>%
        group_by(exp, ppt, strat_use, block_num, trial_in_block) %>%
        summarise(
            angular_dev_m = mean(angular_dev),
            n = n()
        ) %>%
        pivot_wider(
            names_from = strat_use,
            names_prefix = "strat_",
            values_from = angular_dev_m
        ) %>%
        mutate(strategy = strat_1 - strat_0) %>%
        pivot_longer(
            cols = 6:8,
            names_to = "strat_use", values_to = "angular_dev"
        )

    # in strat_use, replace "strat_0" with "Without Strategy"
    # and "strat_1" with "With Strategy",
    # and "strategy" with "Explicit Strategy"
    data <- data %>%
        mutate(strat_use = ifelse(strat_use == "strat_0", "Without Strategy",
            ifelse(strat_use == "strat_1", "With Strategy",
                ifelse(strat_use == "strategy", "Explicit Strategy",
                    strat_use
                )
            )
        ))

    # make strat_use a factor
    data <- data %>%
        mutate(strat_use = factor(strat_use,
            levels = c("Without Strategy", "With Strategy", "Explicit Strategy")
        ))

    # make individual table
    data_ind <- data %>%
        group_by(exp, ppt, strat_use, block_num) %>%
        summarise(
            ind_mean = mean(angular_dev),
            sd = sd(angular_dev),
            ci = vector_confint(angular_dev),
            slope = decay_fit(trial_in_block, angular_dev)[2],
            intercept = decay_fit(trial_in_block, angular_dev)[1],
            n = n(), .groups = "drop"
        )

    # make group table
    data_group <- data_ind %>%
        group_by(exp, strat_use, block_num) %>%
        summarise(
            group_slope_mean = mean(slope),
            slope_ci = vector_confint(slope),
            group_intercept_mean = mean(intercept),
            intercept_ci = vector_confint(intercept),
            n = n(), .groups = "drop"
        )

    # add a nested vector column
    data_group <- data_group %>%
        mutate(trial_in_block = list((c(1:9))))

    # unnest
    data_group <- data_group %>%
        unnest_longer(trial_in_block)

    # make a column with inferred y values
    data_group <- data_group %>%
        mutate(y_inferred = group_slope_mean * trial_in_block +
            group_intercept_mean)

```


## Implicit aftereffect decay
```{r}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- data_ind %>% 
  filter(strat_use == 'Without Strategy') %>%
  ezANOVA(wid = ppt,
        dv = slope, 
        within = .(block_num),
        between = exp,
        detailed = TRUE)

#show and ANOVA + assumptions
print(temp_ANOVA$ANOVA)
```
```{r}
# this is the classical anova equivalent -- numbers are the same as above
summary(aov(slope ~ exp*block_num + Error(ppt/(exp*block_num)),
            data=filter(data_ind, strat_use == 'Without Strategy') ))
```
```{r}
# mixed effects bayes anova
bf = anovaBF(slope ~ exp*block_num + ppt, 
             data=filter(data_ind, strat_use == 'Without Strategy'), 
             whichRandom="ppt")
print(bf)
bayesfactor_inclusion(bf)

```


## With-strategy reach decay
```{r}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- data_ind %>% 
  filter(strat_use == 'With Strategy') %>%
  ezANOVA(wid = ppt,
        dv = slope, 
        within = .(block_num),
        between = exp,
        detailed = TRUE)

#show and ANOVA + assumptions
print(temp_ANOVA$ANOVA)
```
```{r}
# this is the classical anova equivalent -- numbers are the same as above
summary(aov(slope ~ exp*block_num + Error(ppt/(exp*block_num)),
            data=filter(data_ind, strat_use == 'With Strategy') ))
```
```{r}
# mixed effects bayes anova
bf = anovaBF(slope ~ exp*block_num + ppt, 
             data=filter(data_ind, strat_use == 'With Strategy'), 
             whichRandom="ppt")
print(bf)
bayesfactor_inclusion(bf)

```


## Explicit strategy use decay
```{r}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- data_ind %>% 
  filter(strat_use == 'Explicit Strategy') %>%
  ezANOVA(wid = ppt,
        dv = slope, 
        within = .(block_num),
        between = exp,
        detailed = TRUE)
#show and ANOVA + assumptions
print(temp_ANOVA$ANOVA)
```
```{r}
# mixed effects bayes anova
bf <- anovaBF(slope ~ exp*block_num + ppt, 
             data=filter(data_ind, strat_use == 'Explicit Strategy'), 
             whichRandom="ppt")
print(bf)
bayesfactor_inclusion(bf)
```

## Block agnostic implicit aftereffects decay
```{r}
# make individual table
data_blockcollapsed <- data %>%
        group_by(exp, ppt, strat_use) %>%
        summarise(
            ind_mean = mean(angular_dev),
            sd = sd(angular_dev),
            ci = vector_confint(angular_dev),
            slope = decay_fit(trial_in_block, angular_dev)[2],
            intercept = decay_fit(trial_in_block, angular_dev)[1],
            n = n(), .groups = "drop"
        )
```

Descriptive stats
```{r}
# descriptives
data_blockcollapsed %>% 
  filter(strat_use == 'Without Strategy') %>%
  group_by(exp) %>%
  summarise(mean = mean(slope), 
            sd = sd(slope), 
            ci = vector_confint(slope),
            n = n())
```



```{r}
#performing a mixed effects model? (ezANOVA says it can't perform stuff on unbalanced data..)
temp_ANOVA <- data_blockcollapsed %>% 
  filter(strat_use == 'Without Strategy') %>%
  ezANOVA(wid = ppt,
        dv = slope,
        between = exp,
        detailed = TRUE)
```


```{r}
#show and ANOVA + assumptions
print(temp_ANOVA$ANOVA)
```
```{r}
# mixed effects bayes anova
bf = anovaBF(slope ~ exp, 
             data=filter(data_blockcollapsed, strat_use == 'Without Strategy'))
print(bf)
bayesfactor_inclusion(bf)
```

non-ez anova
```{r}
temp_ANOVA <- aov(slope ~ exp, data = filter(data_blockcollapsed, strat_use == 'Without Strategy'))

#show ANOVA + assumptions
print(summary(temp_ANOVA), digits = 6)
eta_squared(temp_ANOVA)
TukeyHSD(temp_ANOVA)
```


```{r, include=FALSE}

tmp_bf_abr_ramp <- bayes_t_test(filter(data_blockcollapsed, strat_use == 'Without Strategy'), "exp", "abrupt", "ramped", "slope")
tmp_bf_stp_ramp <- bayes_t_test(filter(data_blockcollapsed, strat_use == 'Without Strategy'), "exp", "stepped", "ramped", "slope")
tmp_bf_stp_abr <- bayes_t_test(filter(data_blockcollapsed, strat_use == 'Without Strategy'), "exp", "stepped", "abrupt", "slope")
```
```{r}
print(tmp_bf_abr_ramp)
print(tmp_bf_stp_ramp)
print(tmp_bf_stp_abr)
```

```{r, include=FALSE}
# end
```