---
title: "Deprecated analysis code"
output: html_notebook
---




# 2019 Code
### Stepwise experiment


```{r}
p <- nocur_summary %>%
  filter(exp == 'stepwiseExp') %>%
  group_by(rotation_angle, stratuse) %>%
  summarise(mean_dev = mean(mean_devs), 
            ci = vector_confint(mean_devs)) %>%
  ggplot(aes(stratuse, mean_dev, colour = rotation_angle)) +
  geom_beeswarm(data = filter(nocur_summary, exp == 'stepwiseExp'), 
                aes(y = mean_devs, colour = rotation_angle),
                size = 3, alpha = 0.1, groupOnX = TRUE, dodge.width = .5) +
  geom_linerange(aes(ymin = mean_dev - ci, ymax = mean_dev + ci),
                 lwd = 3, alpha = 0.7, position = position_dodge(width = .5)) +
  geom_point(size = 4, alpha = 1, position = position_dodge(width = .5)) +
  # scale_y_continuous(limits = c(-5, 60), 
  #                    breaks = c(0, 15, 30, 45, 60), 
  #                    name = "hand deviation (°)") +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  NULL

p
```

### Long-abrupt experiment

```{r}
p <- 
  nocur_summary %>%
  filter(exp == 'longAbruptExp') %>%
  group_by(stratuse) %>%
  summarise(mean_dev = mean(mean_devs), 
            ci = vector_confint(mean_devs)) %>%
  ggplot(aes(stratuse, mean_dev, colour = "mean + ci")) +
  geom_beeswarm(data = filter(nocur_summary, exp == 'longAbruptExp'), 
                aes(y = mean_devs, colour = "individual ppts"),
                size = 3, alpha = 0.2) +
  geom_linerange(aes(ymin = mean_dev - ci, ymax = mean_dev + ci),
                 lwd = 3, alpha = 0.4) +
  geom_point(size = 3, alpha = 1) +
  scale_y_continuous(limits = c(-5, 60), 
                     breaks = c(0, 15, 30, 45, 60), 
                     name = "hand deviation (°)") +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  scale_color_manual(values=c("#000000", "#FFA47E")) +
  NULL

p
```

### Comparing the 3 groups 
After adapting to the full 60-degree rotations:
```{r}
# p <- 
#   nocur_summary %>%
#   filter(rotation_angle == -60, exp != "abruptExp") %>%
#   group_by(exp, stratuse) %>%
#   summarise(mean_dev = mean(mean_devs), 
#             ci = vector_confint(mean_devs)) %>%
#   ggplot(aes(stratuse, mean_dev, colour = exp)) +
#   geom_beeswarm(data = filter(nocur_summary, rotation_angle == -60, exp != "abruptExp"), 
#                 aes(y = mean_devs, colour = exp),
#                 size = 3, alpha = 0.6, groupOnX = TRUE, dodge.width = .7) +
#   geom_linerange(aes(ymin = mean_dev - ci, ymax = mean_dev + ci),
#                  lwd = 20, alpha = 0.4, position = position_dodge(width = .2)) +
#   geom_point(size = 14, alpha = 1, position = position_dodge(width = .2)) +
#   scale_x_discrete(name = "strategy use", labels = c('without strategy', 'with strategy')) +
#   scale_y_continuous(limits = c(0, 60), breaks = c(0, 15, 30, 45, 60), name = "hand deviation (°)") +
#   theme_minimal() +
#   theme(text = element_text(size=40), 
#         axis.text = element_text(size=40), 
#         legend.text = element_text(size=48), 
#         panel.grid.major.y = element_line(colour = "#ABABAB")) + 
#   scale_colour_manual(values=c("#e51636", "#0500a0", "#0500a0"), 
#                        name= NULL,
#                        breaks=c("stepwiseExp", "abruptExp", "longAbruptExp"),
#                        labels=c("stepwise experiment", "abrupt experiment", "abrupt experiment")) +
#   theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
#   NULL
# 
# p

```




---
# Plots
```{r}
nocur_summary_blocks <- rot_nocur %>%
  group_by(exp, ppt, rotation_angle, block_num, stratuse) %>%
  summarise(mean_devs = mean(angular_dev), 
            sd = sd(angular_dev), 
            ci = vector_confint(angular_dev), 
            n = n()) %>%
  filter((exp == "stepwiseExp" & rotation_angle == -60) | 
           (exp == "longAbruptExp" & (block_num == 1 | block_num == 4)))

nocur_summary_blocks$rotation_angle <- factor(nocur_summary_blocks$rotation_angle, levels=c("-15", "-30", "-45", "-60"))

#add dummy to nocur_summary_blocks
add_dummy <- function(exp_block_df){
  if (exp_block_df[1] == "stepwiseExp")
    return(3)
  else if (exp_block_df[2] == 4)
    return(2)
  else if (exp_block_df[2] == 1)
    return(1)
  else
    return(NaN)
}

nocur_summary_blocks$dummy <- apply(nocur_summary_blocks[ , c("exp", "block_num")], 1, add_dummy)

nocur_summary_blocks
```

## No-cursor plots

```{r}
rot_nocur$block_num <- apply(rot_nocur[ , c("task_num", "exp")], 1, block_num)

nocur_summary_blocks <- rot_nocur %>%
  group_by(exp, ppt, rotation_angle, block_num, stratuse) %>%
  summarise(mean_devs = mean(angular_dev), sd = sd(angular_dev), ci = vector_confint(angular_dev))

nocur_summary_blocks$rotation_angle <- factor(nocur_summary_blocks$rotation_angle, levels=c("-15", "-30", "-45", "-60"))

data <- 
  nocur_summary_blocks %>%
  group_by(exp, block_num, stratuse) %>%
  summarise(mean_dev = mean(mean_devs), 
            ci = vector_confint(mean_devs))

data$block_num <- factor(data$block_num)
nocur_summary_blocks$block_num <- factor(nocur_summary_blocks$block_num)

colourtoUse <- c("#084594", "#2171b5", "#4292c6", "#6baed6",
                 "#940f08", "#b52821", "#c64842", "#D6706b")

p <- data[data$stratuse == 0, ] %>%
  filter(exp != "reintroExp") %>%
  ggplot(aes(block_num, mean_dev, colour = exp)) +
  geom_beeswarm(data = filter(nocur_summary_blocks, stratuse == 0, exp !="reintroExp"), 
                aes(y = mean_devs), size = 3, alpha = 0.6, 
                dodge.width = 0.4) +
  geom_point(size = 14, alpha = 0.6, 
             position = position_dodge(width = .4)) + 
  geom_linerange(aes(ymin = mean_dev - ci, ymax = mean_dev + ci), 
                  lwd = 20, alpha = 0.4, 
                 position = position_dodge(width = .4)) +
  # geom_beeswarm(data = nocur_summary_blocks[nocur_summary_blocks$stratuse == 1, ],
  #               aes(y = mean_devs), size = 3, alpha = 0.15, 
  #               dodge.width = 0.4) +
  # geom_point(data = data[data$stratuse == 1, ], size = 14, alpha = 0.25, 
  #            position = position_dodge(width = .4)) +
  # geom_linerange(data = data[data$stratuse == 1, ],
  #                aes(ymin = mean_dev - ci, ymax = mean_dev + ci),
  #                lwd = 20, alpha = 0.1, 
  #                position = position_dodge(width = .4)) +
  scale_y_continuous(limits = c(0, 50), 
                     breaks = c(0, 15, 30, 45, 60), 
                     name = "hand deviation (°)") +
  scale_x_discrete(name = "block") +
  theme_minimal() +
  theme(legend.position = "none",
    panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  scale_colour_manual(values=c( "#d40000", "#084594", "#8365b5"), 
                       breaks=c("stepwiseExp", "longAbruptExp", "gradualExp"),
                       labels=c( "stepwise", "abrupt", "gradual")) +
  NULL
  
p

p <- p +
    theme(text = element_text(size=40), 
        axis.text = element_text(size=40), 
        legend.text = element_text(size=48))

ggsave(p, height = 14, width = 20, device = "svg", filename = "data/noCur_plot_block.svg")



p <- data[data$stratuse == 1, ] %>%
  filter(exp != "reintroExp") %>%
  ggplot(aes(block_num, mean_dev, colour = exp)) +
  geom_beeswarm(data = filter(nocur_summary_blocks, stratuse == 1, exp !="reintroExp"), 
                aes(y = mean_devs), size = 3, alpha = 0.6, 
                dodge.width = 0.4) +
  geom_point(size = 14, alpha = 0.6, 
             position = position_dodge(width = .4)) + 
  geom_linerange(aes(ymin = mean_dev - ci, ymax = mean_dev + ci), 
                  lwd = 20, alpha = 0.4, 
                 position = position_dodge(width = .4)) +
  # geom_beeswarm(data = nocur_summary_blocks[nocur_summary_blocks$stratuse == 1, ],
  #               aes(y = mean_devs), size = 3, alpha = 0.15, 
  #               dodge.width = 0.4) +
  # geom_point(data = data[data$stratuse == 1, ], size = 14, alpha = 0.25, 
  #            position = position_dodge(width = .4)) +
  # geom_linerange(data = data[data$stratuse == 1, ],
  #                aes(ymin = mean_dev - ci, ymax = mean_dev + ci),
  #                lwd = 20, alpha = 0.1, 
  #                position = position_dodge(width = .4)) +
  scale_y_continuous(limits = c(0, 50), 
                     breaks = c(0, 15, 30, 45, 60), 
                     name = "hand deviation (°)") +
  scale_x_discrete(name = "block") +
  theme_minimal() +
  theme(legend.position = "none",
    panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  scale_colour_manual(values=c( "#d40000", "#084594", "#8365b5"), 
                       breaks=c("stepwiseExp", "longAbruptExp", "gradualExp"),
                       labels=c( "stepwise", "abrupt", "gradual")) +
  NULL
  
p

p <- p +
    theme(text = element_text(size=40), 
        axis.text = element_text(size=40), 
        legend.text = element_text(size=48))

ggsave(p, height = 14, width = 20, device = "svg", filename = "data/withStrat_noCur_plot_block.svg")
```

## Plots for Learning Curves


Below, we plot the learning curves (all reach-to-target tasks with a visible cursor)
```{r}
p <- training_summary %>%
  filter(exp != "reintroExp") %>%
  ggplot(aes(trial_num_cont, mean_devs, colour = exp)) +
  geom_smooth(aes(ymin = mean_devs - ci, ymax = mean_devs + ci, fill = exp),
              stat = "identity", size = 3) +
  scale_y_continuous(limits = c(0, 70), breaks = c(0, 15, 30, 45, 60), 
                     name = "hand deviation (°)") +
  scale_x_continuous(name = "trial") +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major.y = element_line(colour = "#ABABAB")) + 
  scale_fill_manual(values=c("#8365b5", "#084594", "#d40000", "#ffa114"), 
                       breaks=c("longAbruptExp", "stepwiseExP", "gradualExp"),
                      labels=c( "abrupt", "stepwise", "gradual")) +
  scale_colour_manual(values=c("#8365b5", "#084594", "#d40000", "#ffa114"), 
                       breaks=c("longAbruptExp", "stepwiseExP", "gradualExp"),
                       labels=c( "abrupt", "stepwise", "gradual")) +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC")) +
  NULL

p

p <- p +
    theme(text = element_text(size=40), 
        axis.text = element_text(size=40), 
        legend.text = element_text(size=48))

ggsave(p, height = 13, width = 20, device = "svg", filename = "data/LC_plot.svg")
```


Below, we plot the perturbation schedule

```{r}
# load in the csv
pert_sched <- loadData("misc/reach_rotations_csv_forPlotting.csv")

pert_sched <- pert_sched %>%
  pivot_longer(cols = c(abrupt, gradual, stepwise, reintro))


# plot the perturbation schedule (line plot)
p <- pert_sched %>%
  filter(name != "reintro") %>%
  ggplot(aes(x = trial)) +
  geom_smooth(aes(y = value, colour = name),
              stat = "identity", size = 3, alpha = 0.5) +
  scale_y_continuous(limits = c(0, 70), breaks = c(0, 15, 30, 45, 60), 
                     name = "visuomotor rotation (°)") +
  scale_x_continuous(name = "trial",
                     breaks = c(0, 66, 132, 198, 264, 330)) +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.major.y = element_line(colour = "#ABABAB")) +
  scale_colour_manual(values=c( "#d40000", "#084594", "#8365b5"), 
                       breaks=c("stepwise", "abrupt", "gradual"),
                       labels=c( "stepwise", "abrupt", "gradual"))

p

p <- p +
    theme(text = element_text(size=40), 
        axis.text = element_text(size=40), 
        legend.text = element_text(size=48))

ggsave(p, height = 13, width = 20, device = "svg", filename = "data/pert_plot.svg")

```






## By-trial data

We are going to plot the by-trial data to see any effects of time, even on the no-cursor data.

_THIS NEEDS SOME WORK_
```{r}
nocur_trial<- omnibus_nocur %>%
  group_by(exp, task_num, stratuse, trial_num) %>%
  summarise(mean_devs = mean(angular_dev, na.rm = TRUE), 
            sd = sd(angular_dev, na.rm = TRUE), 
            ci = vector_confint(angular_dev,),
            n = n())



```

# Intro plot

```{r}
rep <- 1:4
bond_data <- data.frame("exp" = c(rep_along(rep, "bond")), 
                        "learning" = c(10.9, 12.9, 9.3, 9.66),
                        "error" = c(2.09, 2.86, 3.22, 2.26),
                        "rot_size" = factor(c(15, 30, 60, 90)))

kim_data <- data.frame("exp" = c(rep_along(rep, "kim")), 
                        "learning" = c(18.1, 14.95, 16.35, 11.95),
                        "error" = c(2.4, 2.35, 3.8, 1.9),
                        "rot_size" = factor(c(6, 10, 15, 45)))
shanaa_data <- data.frame("exp" = c(rep_along(rep, "shanaa")), 
                        "learning" = c(14.42, 13.42, 15.64, 12.98),
                        "error" = c(2.5, 1.8, 2.5, 3.1),
                        "rot_size" = factor(c(301, 302, 601, 602)))

intro_data <- rbind.data.frame(bond_data, kim_data, shanaa_data)

# plot
p <- ggplot(data = intro_data, 
            aes(x = rep_along(1:12, factor(c(30, 40, 50, 60))), 
                y = learning, 
                fill = exp)) +
  facet_grid(cols = vars(exp)) +
  geom_bar(stat = "identity", 
           position = position_dodge(1.02),
           colour = "black") +
  geom_errorbar(aes(ymin = learning - error, 
                    ymax = learning + error), width = 0.2,
                position = position_dodge(1.02)) +
  theme_minimal() +
  theme(panel.grid.major.y = element_line(colour = "#CCCCCC"),
        legend.position = "none",
        panel.spacing = unit(9, "lines")) + 
  # scale_fill_manual(values=c( "#084594", "#d40000"), 
  #                      name= NULL,
  #                      breaks=c("longAbruptExp", "stepWiseExP")) +
  scale_y_continuous(limits = c(0, 30), breaks = c(0, 10, 20, 30), 
                     name = "implicit  reach aftereffects (°)") +
  scale_x_discrete(name = "perturbation size (°)") +
  scale_fill_brewer() +
  NULL
              
p

p <- p +
    theme(text = element_text(size=40), 
        axis.text = element_text(size=40), 
        legend.text = element_text(size=48))
  

ggsave(p, height = 10, width = 27, device = "svg", filename = "data/intro.svg")
```

End
```{r}

# pivot for excel stuff (for undergrad projects)
rot_data_wide_reaches <- rot_training %>%
  filter(exp == "longAbruptExp" | exp == "gradualExp") %>%
  select(ppt, exp, trial_num_cont, angular_dev) %>%
  pivot_wider(names_from = ppt, values_from = angular_dev)

# SAVE HERE
fwrite(rot_data_wide_reaches, file = paste("data/wide_format", "reaches.csv", sep = '/'))

# nocursors
rot_data_wide_nocursor <- nocur_summary_blocks %>%
  filter(exp == "longAbruptExp" | exp == "gradualExp") %>%
  select(ppt, exp, block_num, stratuse, mean_devs) %>%
  pivot_wider(names_from = ppt, values_from = mean_devs)

# SAVE HERE
fwrite(rot_data_wide_nocursor, file = paste("data/wide_format", "nocursors.csv", sep = '/'))


## Make JASP-able
set_dummy <- function(exp, trial){
  if(exp == "longAbruptExp") {
    if(trial <= 69)
      return("B_1")
    else if(trial <= 72)
      return("B_2")
    else if(trial >= 322)
      return("B_Last")
    else
      return("X")
  }
  else {
    if(trial <= 70)
      return("B_1")
    else if(trial <= 73)
      return("B_2")
    else if(trial >= 322)
      return("B_Last")
    else
      return("X")
  }
}

JASP_seb_train <- rot_training %>%
  filter(exp == "longAbruptExp" | exp == "gradualExp") %>%
  select(ppt, exp, trial_num_cont, task_num, angular_dev) %>%
  rowwise() %>%
  mutate(dummy = set_dummy(exp, trial_num_cont)) %>%
  filter(dummy != "X") %>%
  group_by(exp, ppt, dummy) %>%
  summarise(mean_dev = mean(angular_dev, na.rm = TRUE), 
            sd = sd(angular_dev, na.rm = TRUE), 
            ci = vector_confint(angular_dev), 
            n = n(), 
            median_dev = median(angular_dev, na.rm = TRUE)) %>%
  select(exp, ppt, dummy, mean_dev) %>%
  pivot_wider(names_from = dummy, values_from = mean_dev)

fwrite(JASP_seb_train, file = paste("data/wide_format", "JASP_seb_LC.csv", sep = '/'))


JASP_seb_NC <- nocur_summary_blocks %>%
  filter(exp == "longAbruptExp" | exp == "gradualExp") %>%
  ungroup() %>%
  select(ppt, exp, block_num, stratuse, mean_devs)

JASP_seb_NC$stratuse <- recode(JASP_seb_NC$stratuse, "0" = "E", "1" = "I")

JASP_seb_NC <- JASP_seb_NC %>%
  pivot_wider(names_from = c(block_num ,stratuse), values_from = mean_devs)

fwrite(JASP_seb_NC, file = paste("data/wide_format", "JASP_seb_NC.csv", sep = '/'))


# end
```
